% \documentclass[a4paper,journal]{IEEEtran}
\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{color, colortbl}
\usepackage{xcolor}
\usepackage{array}
\usepackage{multirow}
\usepackage{footnote}
\usepackage{cite}
%The below is used to add notes to tables without disrupting the IEEEtran format
\usepackage{threeparttable}

% Disable below if wanting to comply exclusively to conference mode of IEEEtran
\IEEEoverridecommandlockouts

\makesavenoteenv{tabular}

%Ignores \vbox errors below the level of 10000
\vbadness=10000
\hbadness=10000
%DIF PREAMBLE EXTENSION ADDED BY LATEXDIFF
%DIF UNDERLINE PREAMBLE %DIF PREAMBLE
\RequirePackage[normalem]{ulem} %DIF PREAMBLE
\RequirePackage{color}\definecolor{RED}{rgb}{1,0,0}\definecolor{BLUE}{rgb}{0,0,1} %DIF PREAMBLE
\providecommand{\DIFadd}[1]{{\protect\color{blue}\uwave{#1}}} %DIF PREAMBLE
\providecommand{\DIFdel}[1]{{\protect\color{red}\sout{#1}}}                      %DIF PREAMBLE
%DIF SAFE PREAMBLE %DIF PREAMBLE
\providecommand{\DIFaddbegin}{} %DIF PREAMBLE
\providecommand{\DIFaddend}{} %DIF PREAMBLE
\providecommand{\DIFdelbegin}{} %DIF PREAMBLE
\providecommand{\DIFdelend}{} %DIF PREAMBLE
%DIF FLOATSAFE PREAMBLE %DIF PREAMBLE
\providecommand{\DIFaddFL}[1]{\DIFadd{#1}} %DIF PREAMBLE
\providecommand{\DIFdelFL}[1]{\DIFdel{#1}} %DIF PREAMBLE
\providecommand{\DIFaddbeginFL}{} %DIF PREAMBLE
\providecommand{\DIFaddendFL}{} %DIF PREAMBLE
\providecommand{\DIFdelbeginFL}{} %DIF PREAMBLE
\providecommand{\DIFdelendFL}{} %DIF PREAMBLE
%DIF END PREAMBLE EXTENSION ADDED BY LATEXDIFF

\begin{document}
%opening
 \title{Localization Procedure for Randomly Deployed WSNs based on the Composability of Position Estimation Protocols}
%   \author{Luis~Sanabria-Russo, Cristina~Cano, Boris Bellalta%
%     \thanks{This research is supported by Universitat Pompeu Fabra, in Barcelona, Spain}}


%A more simple output, useful when involving people from different affiliations
  \author{
      \IEEEauthorblockN{Luis Sanabria-Russo\IEEEauthorrefmark{0}, Cristina Cano\IEEEauthorrefmark{0}, Boris Bellalta\IEEEauthorrefmark{0}}
      \IEEEauthorblockA{\IEEEauthorrefmark{0}Universitat Pompeu Fabra, Barcelona, Spain
      \\\{luis.sanabria, cristina.cano, boris.bellalta\}@upf.edu}
  }

%This is the style of three columns, as indicated in IEEEtran
% \author{\IEEEauthorblockN{Luis Sanabria-Russo}
%  \IEEEauthorblockA{Department of Information\\
%  and Communications Technologies\\
%  Universitat Pompeu Fabra\\
%  Barcelona, Spain\\
%  Email: luis.sanabria@upf.edu}
%  \and
%  \IEEEauthorblockN{Cristina Cano}
%  \IEEEauthorblockA{Department of Information\\
%  and Communications Technologies\\
%  Universitat Pompeu Fabra\\
%  Barcelona, Spain\\
%  Email: cristina.cano@upf.edu}
%  \and
%  \IEEEauthorblockN{Boris Bellalta}
%  \IEEEauthorblockA{Department of Information\\
%  and Communications Technologies\\
%  Universitat Pompeu Fabra\\
%  Barcelona, Spain\\
%  Email: boris.bellalta@upf.edu}}


\maketitle

\begin{abstract}
\boldmath Wireless Sensor Networks (WSNs) are composed of nodes that gather metrics such as temperature, pollution or pressure from events generated by external entities. Localization in WSNs is paramount, given that the collected metrics must be related to the place of occurrence. This work presents an alternative way towards localization in randomly deployed WSNs based on the combination and rearrangement of individual position estimation protocols (\emph{composability}). Our solution provides a flexible approach towards the localization problem in WSNs, which by means of composability it is able to locate more nodes than the individual execution of the modeled protocols while maintaining the same low levels of battery consumption.

%results show a totally distributed localization procedure that achieves a higher number of located nodes than the conventional, individual execution of localization protocols while maintaining the same low levels of battery consumption.

\end{abstract}

\begin{IEEEkeywords}
WSNs, Localization, Multilateration, Bounding-Box.
\end{IEEEkeywords}

\section*{Pending corrections}
It is useful to put the corrections to be made at the beginning of the document, so every time it is seen, you can remember what is left to be done.

\subsection*{First run}
\begin{enumerate}
	\item Before doing any content correction, it is recommended to do a spelling revision.
	\item Define composability at the beginning of the paper to avoid confusions.
	\item Make sure the results are correctly mentioned in the introduction. According to reviewer 2, there is no clear link on how they are achieved.
	\item Redefine what is the main goal of the paper? How does it improve over [3]? I think the main goal is a more flexible solution to the composability of localization protocols.
	\item For the above, reviewer 2 provides the following alternative: how the decision process can be modified? and with what cost? This should be clear if one of the first aim is to allow the use of more localization protocols.

\end{enumerate}


\section{Introduction} \label{introduction}
  \input{section1/intro}

\section{Literature Review} \label{literature}
  \input{section2/literature}

\section{Localization Procedure} \label{locProc}
  \input{section3/locProc}

\section{Evaluation} \label{simulation}
  \input{section4/simulation}

\section{Conclusions} \label{conclusions}
  \input{section5/conclusions}

\bibliographystyle{Classes/IEEEtran}
\bibliography{IEEEabrv,ref}

\end{document}

